---
title: "AI and Coding"
output: html_notebook
---

```{r}
library(Gviz)
library(ggplot2)
library(biomaRt)
library(TxDb.Hsapiens.UCSC.hg38.knownGene)
```

# Coding in R with Copilot Prompt

Learn how to use Copilot to write, debug, and understand R code through prompt-based interactions.
Make sure you have access to Copilot and RStudio.

## Basic R Coding with Prompts

We can use Copilot to helps us write very simple pieces of code, to complex functions and loops, and even entire computer programs!

Copilot Prompt: "Write R code to create a numeric vector with the values 2, 4, 6, 8."
```{r}

```

Print the result
```{r}

```

Copilot Prompt: "Write R code to convert 35 degrees centigrade to Fahrenheit."
```{r}

```

Print the result
```{r}

```


## Advanced R Coding with Prompts

Copilot Prompt: "Write a loop in R to add 2 two every value"
```{r}


```

Copilot Prompt: "Explain how the loop works"

Q. Write the explanation of how the loop works.
Copilot can also be used to help you understand how code works!

Q. Why do we use loops in programming? ask Copilot!

We can also use Copilot to help us write functions in R.

Copilot Prompt: "Can you provide an example of a function in R"
```{r}


```

Copilot Prompt: "Can you give me a function in that squares a list of numbers"
```{r}

```

Q. What is a function ? Why use functions in programming?


Q. Have a go at asking Copilot to write a function of you choosing. what did you come up with?
```{r}

```



# Working with dataframes in R

Copilot Prompt: "Create a data frame in R with columns 'Name', 'Age', and 'Score' using sample data."
```{r}

```

Copilot Prompt: "Save the dataframe to a .csv file in r"
```{r}

```
it's useful to be able to export data to say an Excel file for ease of viewing.

Copilot Prompt: "How do I install the package ggplot2 in R"
```{r}
#install package:

```

Copilot Prompt: "How do I load the package ggplot2 in R"
```{r}
#load ggplot2 package:

```

Copilot Prompt: "Use ggplot2 to create a bar chart of scores by name."
```{r}

```

Copilot Prompt: "Add labels to each bars"

```{r}

```

Copilot Prompt: "Export as a JPEG file"
```{r}

```


Copilot Prompt: "Export as a high resolution publication quality TIFF file"
```{r}

```



# Mini-Porject: How to use copilot for AI assisted data analysis in R 

## Load the Dataset

Copilot Prompt:"Write R code to load and preview the iris dataset."

```{r}

```

ask Copilot how to check the structure of the data
```{r}

```

ask Copilot how to explore the data


## Summary Statistics 

Copilot Prompt: "Generate summary statistics for each variable in the iris data set."

```{r}

```

## Visualize the Data

The following code has been given to you to create a scatter plot comparing Sepal.Length and Petal.Length by species, but it has errors!!!!!, ask copilot nicely to review and fix the code for you:

```{r}
# Load necessary library
library(ggplot)

# Load the iris dataset
data(iris)

# Create scatter plot
ggplot(iris, aes(x = SepalLength, y = Petal.Length, color = Species)) +  
  geom_point(size = 3, alpha = 0.7) +
  labs(
    title = "Sepal Length vs Petal Length by Species",
    x = "Sepal Length (cm)",
    y = "Petal Length (cm)",
    color = "Species"
  ) +
  theme_minimal()

```

Enter the correct working code here:

```{r}

```


Now violin plots are currently very fashionable at the moment in biosciences. Ask copilot to show the code to help you draw a violin plot of the petal length for the different species.
```{r}

```


and a box-plot ?
```{r}

```



## Build a Simple Model

We can perform statistical modelling on our data set and use Copilot to help us perform the analysis and understand what the output signifies.

Copilot Prompt: "Fit a linear regression model predicting Petal.Length using Sepal.Length and Species."
```{r}

```

## Get an Explanation of the Model Output

Ask Copilot to explain the output to you.
Is it a good model? is it significant? are Species and Sepal.Length are strong predictors of Petal.Length ?

## Visualise the Model

Ask Copilot to write the code to visualize regression by species and paste the code here:

```{r}

```

Ask Copilot to help you add confidence bands to the plot

```{r}

```

# Mini-Porject: Analysis of gene expression data

Import the expression data (expression_data.csv)

```{r}

```

View the imported data frame
```{r}

```

Q. How is the data structured?


Perform a t-test on all of the genes, comparing the two groups (SampleA	SampleB	SampleC	SampleD	SampleE	SampleF
 VERSUS SampleG	SampleH	SampleI	SampleJ	SampleK	SampleL)
 
 fix any errors as you go along, ask Copilot to fix any errors!

```{r}

```

Q. Are there any significant genes identified in the analysis ??

Q. Can you draw a box-plot of the result? 

# Mini-Porject: Use copilot to help draw ADAMTS3 gene schematic using Gviz

You may need to go through a few iterations to get the final product, and fix a few errors along the way.
if you have any errors, ask copilot to fix them for you!

```{r}

```

Q. What other pieces of information can you add to your track?

Q. Export your plot to file


# Self-reflection
- What parts of the code did Copilot help with?


- Did you need to alter how you asked copilot the question?


- Did you need to correct or improve any AI-generated code?


- How confident are you in using AI for future coding tasks?


- Do you feel that you need to have a basic understanding of a coding language before using an AI tool for specific tasks?


 